Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-05 ms.tex
starting discussion about revised global parameters

\subsection{Correlation Slopes}

@@

\subsection{Hierarchical Approach?}

>>>>

In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
parameters of the two-component emission model. To derive the 
\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
maps, we employed a correlation slope analysis (see Figure XX). Specifically,
we correlated the observed \PLANCK~data against the appropriate FDS99 
prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
consideration due to the sensitivity of the 100 GHz trend to our ad hoc
low order corrections (see Figure \ref{fig:quad}). All comparisons between
\PLANCK~and the FDS99 predictions were made after smoothing both to 
$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
excellent.

%also emphasize that FDS99 predictions are broadband, not monochromatic
% (i think i can borrow a sentence about this from the absolute zero point 
% section above)

However, the slopes at low frequencies are not precisely unity, as would
be expected if the global two-component parameters derived from FIRAS by
FDS99 were also the best-fitting global parameters with respect to the 
\PLANCK~data set.

% maybe a table listing the correlation slopes and their uncertainties
% would be useful here

We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
the correlation slopes and their uncertainties given in Table QQ by 
taking $T_2$=$16.2$K and running Markov chains to sample the posterior:

Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
strong covariances, but even so several conclusions are clear: (1) a lower 
value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
(3). Because

@@

% at the end of this section state that we do all of our fits etc. with
% both models (call one of them model 1, and the other model 2, similar
% to what FDS99 did

%\subsection{Hierarchical Approach?}
